\Title

### 2020-03-05 manuscript/manuscript.tex
Remove repeated line of R2 score on table
Remove vertical lines from tables

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestAirborneSourceBellowDataConstantDepthDepth
                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
                   & \BestAirborneGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                     & \BestAirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestAirborneGridSourcesConstantDepthPad \\
        Damping & \BestAirborneSourceBellowDataConstantDepthDamping
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping \\
        R$^2$ score & \BestAirborneSourceBellowDataConstantDepthScore
                    & \BestAirborneBlockMedianSourcesConstantDepthScore
                    & \BestAirborneGridSourcesConstantDepthScore \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBellowDataConstantDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c | l l c c}
        \multicolumn{1}{c}{\textbf{Source layout}}
            & \multicolumn{1}{c}{\textbf{Depth type}}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \multicolumn{1}{c}{\textbf{Values}}
            & \multicolumn{1}{c}{\textbf{Increment}} \\
        \hline

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c | l l c c}
        \multicolumn{1}{c}{\textbf{Source layout}}
            & \multicolumn{1}{c}{\textbf{Depth type}}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \multicolumn{1}{c}{\textbf{Values}}
            & \multicolumn{1}{c}{\textbf{Increment}} \\
        \hline

>>>>

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestAirborneSourceBellowDataConstantDepthDepth
                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
                   & \BestAirborneGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                     & \BestAirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestAirborneGridSourcesConstantDepthPad \\
        Damping & \BestAirborneSourceBellowDataConstantDepthDamping
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBellowDataConstantDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c l l c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values}
            & \textbf{Increment} \\
        \hline

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c l l c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values}
            & \textbf{Increment} \\
        \hline
